\cvsection{Professional Experience}

\begin{cvexperience}

\experience
    {Autolab}
    {Full Stack Software Engineer}
    {Bogotá, Colombia}
    {October 2021 -- May 2026}

\project
{Fleet Management Portal}
{
    \achievement{Designed and developed user interfaces for the Fleet Management Portal, enabling enterprise customers to manage maintenance operations, quotations, appointments, and fleet administration through intuitive business workflows.}

    \achievement{Architected a modular frontend application with reusable components, role-based interfaces, dashboards, and scalable features while integrating seamlessly with backend services.}
}

\project
{CRM Platform}
{
    \achievement{Modernized legacy frontend modules by introducing reusable components, improving maintainability, and reducing technical debt across the CRM platform.}

    \achievement{Developed business features for warranties, quotations, workshop administration, and operational management with a strong focus on usability and workflow efficiency.}

    \achievement{Integrated frontend applications with REST APIs and automated WhatsApp communication features to improve operational processes and user experience.}
}

\project
{Backend Services}
{
    \achievement{Designed and implemented REST APIs and business logic supporting both the CRM Platform and Fleet Management Portal.}

    \achievement{Developed reusable SQLAlchemy query builders, optimized PostgreSQL queries, and centralized shared backend components to improve maintainability and performance.}
}

\project
{Production Support}
{
    \achievement{Investigated and resolved production issues affecting frontend applications by analyzing user reports, Sentry logs, and backend integrations.}

    \achievement{Collaborated with cross-functional teams to diagnose and fix issues across frontend, backend, and database layers.}
}

\end{cvexperience}