\cvsection{Professional Experience}

\begin{cvexperience}

\experience
    {Autolab}
    {Full Stack Software Engineer}
    {Bogotá, Colombia}
    {October 2021 -- May 2026}

\project
{Backend Platform}
{
    \achievement{Designed and developed REST APIs using Python, Flask and SQLAlchemy to support enterprise applications for vehicle maintenance and fleet management.}

    \achievement{Designed PostgreSQL schemas, optimized complex SQL queries, and developed reusable data access components, improving application performance and maintainability.}

    \achievement{Built reusable backend services and shared business logic that reduced code duplication and standardized development across multiple products.}
}

\project
{Fleet Management Platform}
{
    \achievement{Designed and implemented backend services supporting fleet maintenance workflows, quotation approvals, appointment management and operational communication for enterprise customers.}

    \achievement{Architected modular backend components with role-based access control and scalable domain separation, enabling future service evolution and improving maintainability.}
}

\project
{CRM Platform}
{
    \achievement{Refactored legacy backend modules by centralizing business rules, reducing technical debt and improving long-term maintainability.}

    \achievement{Developed backend functionality for warranties, quotations, workshop administration and operational management.}

    \achievement{Automated operational workflows through WhatsApp integrations, reducing manual communication between advisors, workshops and fleet customers.}
}

\project
{Production Support}
{
    \achievement{Investigated and resolved production incidents using Sentry, SQL analysis and application logs across backend, database and frontend components.}

    \achievement{Performed root cause analysis and implemented long-term fixes to improve application stability and reliability.}
}

\end{cvexperience}