\cvsection{Professional Experience}

\begin{cvexperience}

\experience
    {Autolab}
    {Full Stack Software Engineer}
    {Bogotá, Colombia}
    {October 2021 -- May 2026}

\project
{Fleet Management Portal}
{
    \achievement{Designed and developed the Fleet Management Portal, automating fleet maintenance workflows, quotation approvals, appointment tracking, and operational communication for enterprise customers.}

    \achievement{Architected an independent frontend and backend module with role-based access control, scalable architecture, dashboards, and fleet administration features, improving maintainability and enabling future service separation.}
}
\project
{CRM Platform}
{
    \achievement{Modernized legacy CRM modules through refactoring, reusable components, and centralized business logic, improving maintainability and reducing technical debt.}

    \achievement{Designed and implemented business features for warranties, quotations, workshop administration, and operational management.}

    \achievement{Automated operational workflows by integrating WhatsApp notifications and reducing manual communication between advisors, workshops, and fleet customers.}
}

\project
    {Backend Platform}
{
    \achievement{Designed PostgreSQL tables, REST APIs and reusable SQLAlchemy query builders.}
    \achievement{Optimized complex SQL queries reducing execution time and infrastructure costs.}
    \achievement{Developed reusable query builders and shared backend components that reduced code duplication and standardized data access.}
}

\project
    {Production Support}
{
    \achievement{Provided production support by analyzing incidents reported through Sentry and business teams.}
    \achievement{Diagnosed and resolved production issues across frontend, backend and database layers.}
}

\end{cvexperience}