\cvsection{Professional Experience}

\begin{cvexperience}

\experience
    {Autolab}
    {Full Stack Software Engineer}
    {Bogotá, Colombia}
    {October 2021 -- May 2026}

\project
{Fleet Management Portal}
{
    \achievement{Designed and developed the Fleet Management Portal, delivering frontend and backend features that automated fleet maintenance workflows, quotation approvals, appointment tracking and operational communication for enterprise customers.}

    \achievement{Architected modular frontend and backend components with role-based access control, dashboards and scalable business modules, improving maintainability and enabling future service separation.}
}

\project
{CRM Platform}
{
    \achievement{Modernized legacy CRM modules through reusable frontend components, backend refactoring and centralized business logic, improving maintainability and reducing technical debt.}

    \achievement{Designed and implemented business features for warranties, quotations, workshop administration and operational management across frontend and backend layers.}

    \achievement{Automated operational workflows by integrating WhatsApp notifications and reducing manual communication between advisors, workshops and fleet customers.}
}

\project
{Backend Services}
{
    \achievement{Designed and developed Python backend services using Flask, implementing business logic and REST APIs supporting both the CRM Platform and Fleet Management Portal.}

    \achievement{Designed PostgreSQL data models, developed reusable SQLAlchemy query builders, optimized complex SQL queries and centralized shared backend components to improve performance and maintainability.}
}

\project
{Production Support}
{
    \achievement{Provided production support by investigating incidents reported through Sentry and business teams across frontend, backend and database layers.}

    \achievement{Diagnosed and resolved production issues while collaborating with cross-functional teams to maintain software reliability and operational continuity.}
}

\end{cvexperience}